---
title: "Product Pricing Algorithm"
author: "Steven Ponce - Business Science Part 1"
date: "2022-05-02"         ## `r Sys.Date()` current date 
output:
  html_document: 
    toc: TRUE
    df_print: paged
    theme: flatly
    highlight: tango
    pdf_document: default
params:
  interactive: TRUE 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    message = FALSE,
    warning = FALSE,
    out.width = "100%")
```

```{r}
library(tidyverse)
library(tidyquant)
library(parsnip)
library(plotly)
```         


```{r}
source('../00_scripts/separete_bikes_and_outlier_detection.R')
source("../00_scripts/plot_product_recommendation.R")
```

```{r}
bike_orderlines_tbl <- read_rds("../00_data/bike_sales/data_wrangled/bike_orderlines.rds")
```

```{r}
models_tbl <- read_rds("../00_models/parsnip_models_tbl.rds")
```

## Problem Statement

Research and Development wants help to determine new product ideas and pricing using existing product line as a benchmark.

## Solution Summary

We've identified several product gaps in the existing product line including:

1. Aluminum Over Mountain

2. Aluminum Triathalon

The Data Science Team has develop a pricing model that uses predictive analytics to estimate the price of the new bicycle models based on the existing fleet. This ensure that new models are priced comparativeky to other similar bicycles.

New product prediction for 2 new models:

1. Trigger, Over Mountain with Aluminum Frame: $2,508

2. Slice, Triathalon with Aluminum Frame: $2,231

**Next Steps:** Integrate the model into a proof-of-concept web aplication that can be deployed to the R&D department.


## Gap Analysis

### Bike List

Our current product portfolio consist of 97 bike models that are analyzed.

```{r}
get_bike_features()
```

### Gaps

This visualization segments the full bicycle product line by category and frame material.  This exposes two product gaps:

1. New **Aluminum** line of bikes in the **Over Mountain Category**

2. New **Aluminum** line of bikes in the **Triathlon**


```{r, out.height="600px"}
plot_bike_features(interactive = params$interactive)
```
 
\newpage
## Price Prediction

New product prediction for 2 new models:

1. Trigger, Over Mountain with Aluminum Frame: $2,508

2. Slice, Triathalon with Aluminum Frame: $2,231



```{r}
# CREATE NEW MODELS
new_over_mountain_trigger <- tibble(
    model = "Trigger Al 1",
    frame_material = "Aluminum",
    category_2 = "Over Mountain",
    model_base = "Trigger",
    model_tier = "Aluminum 1",
    black      = 0,
    hi_mod     = 0,
    team       = 0,
    red        = 0,
    ultegra    = 0,
    dura_ace   = 0,
    disc       = 0
) 

new_triathalon_slice_tbl <- tibble(
    model = "Slice Al 1",
    frame_material = "Aluminum",
    category_2 = "Triathalon",
    model_base = "Slice",
    model_tier = "Ultegra",
    black      = 0,
    hi_mod     = 0,
    team       = 0,
    red        = 0,
    ultegra    = 0,
    dura_ace   = 0,
    disc       = 0
) 

new_bikes_tbl <- bind_rows(new_over_mountain_trigger, 
                           new_triathalon_slice_tbl)

# new_bikes_tbl
```

```{r}
# GET XGBOOST MODEL

model_07_xgboost <- models_tbl %>% 
    filter(model_id %>% str_detect('XGBOOST')) %>% 
    pull(model) %>% 
    # extract the 1st element of the list
    pluck(1)  
```


```{r}
# OUTPUT PREDICTIONS IN A TABLE

model_07_xgboost %>% 
    predict(new_bikes_tbl) %>% 
    mutate(.pred = scales::dollar(.pred, accuracy = 1)) %>% 
    bind_cols(new_bikes_tbl) %>% 
    gather(key = 'New Model Attribute', value = 'value', -model, factor_key = TRUE) %>% 
    spread(key = model, value = value) #%>% 
    
    # for PDF report, we can use
    # knitr::kable()
```

