---
title: "Week 3 Challenge"
author: "Business Science"
date:   "12/30/2018"
output: 
    html_document:
        toc: TRUE
        theme: flatly
        highlight: tango
        code_folding: show
        df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Challenge Summary

This is a short challenge to begin applying what you are learning to the problem at hand. You will go through a series of questions related to the course project goals: 

1. Coming up with a new product idea, and 

2. Segmenting the customer-base

# Objectives

1. Apply `lubridate` and `stringr` functions to answer questions related to the course projects. 

2. Gain exposure to `rmarkdown`.

# Data

To read the data, make sure that the paths point to the appropriate data sets. Saving the file in the "challenges folder" should enable the paths to be detected correctly. 

```{r, message=FALSE, warning=FALSE}
# Load libraries
library(tidyverse)
library(lubridate)
```

```{r}
# Read bike orderlines data
path_bike_orderlines <- "../00_data/bike_sales/data_wrangled/bike_orderlines.rds"
bike_orderlines_tbl <- read_rds(path_bike_orderlines) %>%
    
    # Fix typos found in Feature Engineering
    mutate(model = case_when(
        model == "CAAD Disc Ultegra" ~ "CAAD12 Disc Ultegra",
        model == "Syapse Carbon Tiagra" ~ "Synapse Carbon Tiagra",
        model == "Supersix Evo Hi-Mod Utegra" ~ "Supersix Evo Hi-Mod Ultegra",
        TRUE ~ model
    ))

glimpse(bike_orderlines_tbl)
```



# Questions

# lubridate: Which month has the highest bike sales? (Difficulty = Medium)

- Start with `bike_orderlines_tbl`
- Select columns `order_date` and `total_price`
- Add a column called `month`
- Group by, summarize, and ungroup calculating the `sales`
- Arrange the sales values by month (Jan - Dec)
- Format the sales values as `dollar()`
- Adjust column names to title case

_What does this tell us about a time of year to focus marketing efforts?_

```{r}
bike_orderlines_tbl %>% 
    select(order_date, total_price) %>% 
    mutate(
        order_date = ymd(order_date),
        month = month(order_date, label = TRUE)
    ) %>% 
    
    group_by(month) %>% 
    summarise(
        sales = sum(total_price) 
    ) %>% 
    
    ungroup() %>% 
    mutate(sales = scales::dollar(sales)) %>% 
    arrange(month) %>% 
    rename(
        Month = month,
        Sales = sales
    )

```


# stringr: What is the median orderline sales value by Bike Attribute? (Difficulty = Medium)

- Begin with `bike_orderlines`
- Select `model` and `total_price`
- Detect if string is present (e.g. "black inc")
- Groupby, summarize, and ungroup calculating the `median()` orderline
- Format numeric price as `dollar()` (Hint: investigate `largest_with_cents` argument)
- Rename column to evaluation string (e.g. "Black Inc") 


Evaluate "Black Inc". _What does this tell us about the "Black Inc" feature?_

```{r}
bike_orderlines_tbl %>% 
    
    select(model, total_price) %>% 
    
    # flag / boolean 
    mutate(
        `Black Inc` =  str_detect(str_to_lower(model), 'black inc')
    ) %>% 
    
    group_by(`Black Inc`) %>% 
    summarise(
        `Median Orderline` = median(total_price)
    ) %>% 
    
    ungroup() %>% 
    mutate(
        `Median Orderline` =  scales::dollar(`Median Orderline`)
    ) %>% 

    arrange()
    
```

Evaluate "Ultegra". _What does this tell us about the "Ultegra" feature?_

```{r}
bike_orderlines_tbl %>% 
    
    select(model, total_price) %>% 
    
    # flag / boolean 
    mutate(
        Ultegra =  str_detect(str_to_lower(model), 'ultegra')
    ) %>% 
    
    group_by(Ultegra) %>% 
    summarise(
        `Median Orderline` = median(total_price)
    ) %>% 
    
    ungroup() %>% 
    mutate(
        `Median Orderline` =  scales::dollar(`Median Orderline`)
    ) %>% 

    arrange()
    
```


Evaluate "Disc" option. _What does this tell us about the "Disc" feature?_

```{r}
bike_orderlines_tbl %>% 

    select(model, total_price) %>% 
    
    # flag / boolean 
    mutate(
        Disc =  str_detect(str_to_lower(model), 'disc')
    ) %>% 
    
    group_by(Disc) %>% 
    summarise(
        `Median Orderline` = median(total_price)
    ) %>% 
    
    ungroup() %>% 
    mutate(
        `Median Orderline` =  scales::dollar(`Median Orderline`)
    ) %>% 

    arrange()

```


# stringr: What are the average, min, and max prices by Base Model? (Difficulty = High)

- Start with `bike_orderlines_tbl`
- Select distinct primary category, secondary category, model, and price (unit price, not total price)
- Create the base feature, `model_base` (Hint: Use the Feature Engineering code)
    - separate the models
    - Create a base feature that combines the appropriate parts (e.g. "Beast of the East")
- Remove any unnecessary columns (Hint: Deselect any columns matching `"model_[0-9]"`)
- Group by, summarize, and ungroup (Hint: use `mean()`, `min()`, and `max()`)
- Arrange descending by average price
- Format any numeric columns as `dollar()` (Hint: Check out `largest_with_cents`) 
- Adjust the column names to title case

_What does this tell us about how bikes are priced?_

```{r}
bike_orderlines_tbl %>% 
    
    select(category_1, category_2, model, price) %>% 
    
    # separate model col into more columns
    separate(col    = model, 
             into   = str_c('model_', 1:6),
             sep    = ' ', 
             remove = FALSE,
             fill   = 'right',
             extra  = 'drop') %>% 
    
    # create a 'base' feature - notice `beat of the east` case
    mutate(
        model_base = case_when(
            
            # fix `Supersix  Evo`
            str_detect(str_to_lower(model_1), 'supersix') ~ str_c(model_1, model_2, sep = ' '),
            
            # fix `Fat CAAD`
            str_detect(str_to_lower(model_1), 'fat') ~ str_c(model_1, model_2, sep = ' '),
            
            # fix `Beast of the East`
            str_detect(str_to_lower(model_1), 'beast') ~ 
                str_c(model_1, model_2, model_3, model_4, sep = ' '),
            
            # fix `Bad Habit`
            str_detect(str_to_lower(model_1), 'bad') ~ str_c(model_1, model_2, sep = ' '),
            
            # fix `Scapel 29`
            str_detect(str_to_lower(model_2), '29') ~ str_c(model_1, model_2, sep = ' '),
            
            # catch all
            TRUE ~ model_1)
        ) %>% 
    
    # remove unnecessary columns
    select(-matches('model_[0-9]')) %>% 
    
    # group and summary
    group_by(category_1, category_2, model_base) %>% 
    summarise(
        avg_price = mean(price),
        min_prince = min(price),
        max_price = max(price)
    ) %>% 
    ungroup %>% 
    arrange(desc(avg_price))

    ### Almost done - I need to rename columns and add the dollar scale  ###
 
```




